DRAFT

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

### • Some value are non-zero but include zeros. The next table checks the zero values and the quantity of unique values.
```{r}
kable(funModeling::df_status(df))
```

>>>>

### • Some value are not blank but include zeros and inf. The next table checks these entries as well as unique values.
```{r echo=FALSE, include=FALSE}
zeros<-funModeling::df_status(df2)
```

```{r echo=FALSE, include=TRUE}
kable(zeros)
```
